An Example of the 2014 IEEE Aerospace Conference Paper Format Using a \LaTeX~Enivronment

### 2018-06-09 Conference/ASC 2014/Example.tex
added Conference folder

\usepackage{amsmath,amssymb,url}
\usepackage{graphicx,subfigure,tikz}
\usepackage{color}
\usepackage{wrapfig}
\usepackage{epstopdf}
\newcommand{\ignore}[1]{}  % {} empty inside = %% comment

\newcommand{\norm}[1]{\ensuremath{\left\| #1 \right\|}}
\newcommand{\bracket}[1]{\ensuremath{\left[ #1 \right]}}
\newcommand{\braces}[1]{\ensuremath{\left\{ #1 \right\}}}
\newcommand{\parenth}[1]{\ensuremath{\left( #1 \right)}}
\newcommand{\pair}[1]{\ensuremath{\langle #1 \rangle}}
\newcommand{\met}[1]{\ensuremath{\langle\langle #1 \rangle\rangle}}
\newcommand{\refeqn}[1]{(\ref{eqn:#1})}
\newcommand{\reffig}[1]{Fig. \ref{fig:#1}}
\newcommand{\tr}[1]{\mathrm{tr}\ensuremath{\negthickspace\bracket{#1}}}
\newcommand{\trs}[1]{\mathrm{tr}\ensuremath{[#1]}}
\newcommand{\ave}[1]{\mathrm{E}\ensuremath{[#1]}}
\newcommand{\deriv}[2]{\ensuremath{\frac{\partial #1}{\partial #2}}}
\newcommand{\SO}{\ensuremath{\mathsf{SO(3)}}}
\newcommand{\T}{\ensuremath{\mathsf{T}}}
\renewcommand{\L}{\ensuremath{\mathsf{L}}}
\newcommand{\so}{\ensuremath{\mathfrak{so}(3)}}
\newcommand{\SE}{\ensuremath{\mathsf{SE(3)}}}
\newcommand{\se}{\ensuremath{\mathfrak{se}(3)}}
\renewcommand{\Re}{\mathbb{R}}
\newcommand{\aSE}[2]{\ensuremath{\begin{bmatrix}#1&#2\\0&1\end{bmatrix}}}
\newcommand{\ase}[2]{\ensuremath{\begin{bmatrix}#1&#2\\0&0\end{bmatrix}}}
\newcommand{\D}{\ensuremath{\mathbf{D}}}
\renewcommand{\d}{\ensuremath{\mathfrak{d}}}
\newcommand{\Sph}{\ensuremath{\mathsf{S}}}
\renewcommand{\S}{\Sph}
\newcommand{\J}{\ensuremath{\mathbf{J}}}
\newcommand{\Ad}{\ensuremath{\mathrm{Ad}}}
\newcommand{\intp}{\ensuremath{\mathbf{i}}}
\newcommand{\extd}{\ensuremath{\mathbf{d}}}
\newcommand{\hor}{\ensuremath{\mathrm{hor}}}
\newcommand{\ver}{\ensuremath{\mathrm{ver}}}
\newcommand{\dyn}{\ensuremath{\mathrm{dyn}}}
\newcommand{\geo}{\ensuremath{\mathrm{geo}}}
\newcommand{\Q}{\ensuremath{\mathsf{Q}}}
\newcommand{\G}{\ensuremath{\mathsf{G}}}
\newcommand{\g}{\ensuremath{\mathfrak{g}}}
\newcommand{\Hess}{\ensuremath{\mathrm{Hess}}}
\newcommand\circled[1]{%
  \tikz[baseline=(C.base)]\node[draw,circle,inner sep=0.5pt](C) {#1};\!
}

\newtheorem{prop}{Proposition}

\newcommand{\EditTL}[1]{{\color{blue}\protect #1}}
%\newcommand{\EditTL}[1]{{\protect #1}}

\begin{document}
\title{Design and Development of a Free-Floating\\ Hexrotor UAV for 6-DOF Maneuvers}

\author{%
Evan Kaufman, Kiren Caldwell, Daewon Lee and Taeyoung Lee\\ 
Mechanical and Aerospace Engineering\\
George Washington University\\
Washington, DC 20052\\
202-994-8710\\
\{evankaufman, kiranimo, daewonlee, tylee\}@gwu.edu
%\and 
%Jane Smith\\
%Department of ECE\\
%University of Nowhere\\
%Nowhere, ZS 99999\\
%888-888-8888\\
%jane.smith@nowhere.edu
%%%% IMPORTANT: Use the correct copyright information--IEEE, Crown, or U.S. government. %%%%%
%\thanks{\footnotesize 978-1-4799-1622-1/14/$\$31.00$ \copyright2014 IEEE.}              % This creates the copyright info that is the correct 2012 data
%\thanks{{978-1-4799-1622-1/14/$\$31.00$ \copyright2014 Crown.}}          % Use this copyright notice only if you are employed by a crown government (e.g., Canada, UK, Australia)
%\thanks{{U.S. Government work not protected by U.S. copyright.}}         % Use this copyright notice only if you are employed by the U.S. Government.
%%%%% Use this footnote to keep track of your paper number/versioning.
\thanks{{\bf 978-1-4799-1622-1/14/\$31.00 \copyright2014 IEEE}} % NOTE: Modify this line to reflect your paper number, version, and date of version for tracking purposes.
}

@@

\begin{abstract}
This paper presents design and development of an experimental testbed for nonlinear geometric controls of a rigid body. We develop a fully actuated hexrotor UAV that uses six variable pitch propellers to control six degrees of freedom maneuvers, namely three position and three attitude variables, independently. In contrast to the popular quadrotor UAVs that can hover at a single attitude, the hexrotor presented in this paper is capable of hovering at any attitude provided that thrust is sufficiently large. A geometric controller is also developed on the special Euclidean group to track given desired position and attitude trajectories under the effects of unknown disturbances. These are particularly useful for ground tests for large angle rotational dynamics of spacecraft that are combined with arbitrary translational motions. A numerical example that involves a nontrivial maneuver and preliminary experimental tests are also presented.
%
%
%It is well known that a controller that considers the geometric properties of the special euclidean group  explicitly may be applied to a fully-actuated system; this paper provides a technique to validate this controller, particularly to model rotations in spacecraft maneuvers.  We present a numerical example that involves a nontrivial trajectory and preliminary experimental results.
\end{abstract}

@@

\section{Introduction}

Quadrotor UAVs have become popular recently due to their simple mechanical structure and aggressive maneuverability. However, a quadrotor can only hover at a single attitude where the plane of its rotors is orthogonal to gravity. This restriction causes the attitude dynamics to be coupled with the translational dynamics, yielding a platform not conducive to spacecraft attitude control problems that involve arbitrary rotational maneuvers or de-tumbling. Other spacecraft attitude control testbeds such as spherical air-bearings exhibit limited operation angles, restricting the attitude maneuverability. These limitations present difficulty in testing large angle rotational maneuvers of rigid bodies.

% Background and motivation
	% Quadrotor UAV
		% Simpler mechanical structure, hovering capability at a single attitude
		% Attitude dynamics is coupled to translational dynamics
	% Spacecraft attitude control testbed
		% Spherical air-bearing
		% Limited operation angle
	% Limited maneuverability
	% Difficultly to test large angle rotational maneuver of a rigid body

The goal of this paper is to design an experimental testbed for spacecraft control systems using a free-floating six degrees-of-freedom (DOF) UAV. This proposed design would allow for decoupled large angle rotational maneuvers and aggressive translational maneuvers.

% Goal
	% Experimental testbed for a free-floating, 6 DOF UAV
	% Decoupled large angle rotational maneuver and aggressive translational maneuver

The configuration of the rotor planes for a class of nonplanar UAVs that exhibits 6 DOF control is described in~\cite{CroLanGCD11}. Here, the attitude control is developed in terms of quaternions and is considered over a limited region near hover. The use of variable pitch propellers is analyzed theoretically without experimental validation on a free-floating UAV, which is a primary contribution of this paper. The prospect of a 6 DOF UAV is additionally explored in~\cite{ZouCheITJ13}, but the focus of this research is development of an adaptive neuro fuzzy inference system, which avoids the nonlinearities of attitude dynamics that the geometric controller presented in this paper explicitly considers.

% Prior work
	%\item Two references to papers involving fully-actuated hexrotors, but issues and limitations with quaternions and fixed pitch propellers

The contribution of this paper involves two primary aspects: a hardware development of 6 DOF UAV and implementation of a geometric nonlinear controller. An experimental evaluation of a variable pitch propeller system is presented, which allows for thrust in two directions. Experimentation of this actuator is used to determine admissible regions of hover.

A geometric controller is chosen for the hexrotor UAV to avoid issues that arise with controllers developed in terms of Euler angles or quaternions. Control systems for quadrotors based on Euler angles, such as those developed in~\cite{GueHamPIICCA05} and~\cite{BouSiePIICRA05}, exhibit singularities when representing complex rotational maneuvers, thereby significantly restricting their ability to achieve complex flight maneuvers. The hexrotor controller in~\cite{CroLanGCD11} is based on quaternions, which do not have singularities. However, quaternions have ambiguities in representing an attitude, as with the three-sphere, the unit-vectors in ${\Re}^4$, doublecover the attitude configuration of the special orthogonal group. Therefore, a single physical attitude of a rigid body may yield two different control inputs, which causes inconsistency in the resulting control system. A specific choice between two quaternions generates a discontinuity that
makes the resulting control system sensitive to noise and disturbances~\cite{MaySanPICDC09}. It is possible to construct continuous controllers, but they may exhibit unwinding behavior, where the controller unnecessarily rotates a rigid body through large angles, even if the initial attitude is close to the desired attitude, thereby breaking Lyapunov stability~\cite{BhaBerSCL00}.

To avoid singularities and ambiguities associated with local coordinates to represent attitude, we present geometric controller directly on the nonlinear configuration manifold of the special Euclidean group. %In~\cite{LeeLeoPICDC10,LeeITCST13}, geometric controllers have been applied to quadrotor systems, but never on fully-actuated systems such as the one presented in this paper. 
The controller can be shown to exhibit almost global exponential stability with rigorous Lyapunov stability analysis. Furthermore, a generalized integral term is included in the controller to guarantee robustness with respect to unstructured disturbances.

The hexrotor hardware and geometric controller presented in this paper are particularly useful for large angle rotational maneuvers to model spacecraft attitude controls. Such synergistic combination of abstract nonlinear control theory and advanced hardware design to construct an experimental platform for arbitrary translational and rotational maneuvers of spacecraft model is the main contribution of this paper.

The paper is organized as follows: the hexrotor UAV dynamics are formally presented in Section \ref{sec:Dynamics}.
The geometric controller is formulated and stability is analyzed in Section \ref{sec:Control}.
Section \ref{sec:Hardware} outlines the hardware development of the actuators and sensors, in addition to software structure and preliminary experimental tests.

% to produce a fully-actuated system.
%The software structure and preliminary experimental results are presented in Section \ref{sec:Experiment}.

% Our approach
	% Hardware development
		% Variable pitch propeller
		% Determination of admissible region 
	% Geometric controller
		% Minimal attitude representation such as Euler-angle: singularity
		% Quaternion: ambiguity
		% Geometric control on SE(3): avoid singularity and ambiguity
			% Stability analysis to show almost global exponential stability
			% Additional generalized integral term for robustness
			% Useful for large-angle rotational maneuvers

% Paper Organization

\section{Dynamics of Hexrotor UAV}\label{sec:Dynamics}

\subsection{Configuration of Hexrotor UAV}

Consider the hextrotor UAV illustrated in Figure \ref{fig:hexrotorDiagram}. The hexrotor UAV contains $6$ propeller actuators, located in a hexagon configuration such that $6$ coplanar arms hold each propeller. We define two orthonormal frames, namely the inertial reference frame $\{\vec e_1,\vec e_2,\vec e_3\}$ and the body-fixed frame $\{\vec b_1,\vec b_2,\vec b_3\}$. The inertial frame is fixed with respect to the Earth, and the third axis $\vec e_3$ is parallel to the direction of gravity. The origin of the body-fixed frame lies at the hexrotor center of mass. The body-fixed frame is defined such that the first body-fixed axis $\vec b_1$ aligns with arm $1$, and the second axis $\vec b_2$ points between arms $2$ and $3$, i.e., the plane of arms is spanned by $\{\vec b_1,\vec b_2\}$. The third body-fixed axis $\vec b_3$ is defined using the right hand rule, and it is normal to the plane of arms. Due to the symmetry of a hexagon, arms on opposite sides of the UAV are aligned. Even though the arm configuration is planar, the rotor planes are inclined such that two propellers occupy each of three orthogonal planes spanned by the body-fixed axes. Opposite arms hold propellers that share the same plane. This rotor configuration serves to generate the total thrust in any direction with respect to the body-fixed frame while achieving the moment balance.

Several assumptions are made to generate a dynamic model for the hexrotor UAV. We consider that the components of the frame are rigid. The actuators are assumed to be capable of generating thrust arbitrarily in both positive and negative directions. It is further assumed that the thrust of each propeller is directly controlled and the dynamics of rotors are not considered. Therefore, the thrust of each propeller is considered as the control input in this paper. These assumptions are common in the existing dynamic models of multirotor UAVs~\cite{TayMcGITCSTI06,CasLozICSM05}, and the presented control system can readily be extended to include linear rotor dynamics, as studied in~\cite{BouSiePIICRA05}.

%Furthermore, the rotor dynamic model is not considered in the controller design; hence actuator tests serve to substitute this information when designing output parameters to the motors and propellers.

Let $x\in{\Re}^3$ be the location of the mass center represented with respect to the inertial frame, and let $R\in\SO$ be the rotation matrix that represents the attitude of the hexrotor UAV. It is defined as the linear transformation of the representation of a vector from the body-fixed frame to the inertial frame. Here, the special orthogonal group is defined as
\begin{align*}
{\SO}=\{R \in{\Re}^{3\times3}\mid R^T R=I,\; \det{R}=1\}.
\end{align*}
Therefore, the configuration space of the hexrotor UAV is the special Euclidean group $\SE$ which is the semidirect product of ${\Re}^3$ and $\SO$~\cite{MarRat99}.

%The, the configuration of the hexrotor UAV is defined by $(x,R)\in\SE$,

%Both reference frames consist of a triad of orthogonal vectors, so these frames are taken as basis sets in ${\Re}^3$. These orthonormal vectors can be combined into $3\times3$ real matrices that represent linear transformations between the vector spaces of the two frames.
%The hexrotor UAV configurations can be defined completely with the location of the UAV center of mass and its attitude with respect to the inertial reference frame. The special Euclidean group $\SE$ is chosen as the configuration manifold, which is a semidirect product of ${\Re}^{3}$ position vector and the special orthogonal group $\SO=\{R\in{\Re}^{3\times3}\mid R^TR, \det{R}=1\}$ attitude configuration.

	% Inertial frame and body fixed frame
	% Hexrotor diagram
	% Hexrotor configuration
		% 6 rotors at the end of arms
		% rotor planes are inclined
	% Assumptions
		% rigid body
		% thrust can be generated arbitrarily in both direction
		% no rotor dynamic model
	% Configuration space: SE(3)

\begin{figure}
\centerline{
	\setlength{\unitlength}{0.1\columnwidth}\scriptsize
\begin{picture}(7,5.5)(0,0)
\put(.4,1){\includegraphics[width=0.7\columnwidth]{uav_complete.jpg}}
\thicklines
\put(1, 1.5){\vector(4, 1){.8}}
\put(2,1.75){\shortstack[c]{$\vec e_{1}$}}
\put(1, 1.5){\vector(3, -2){.8}}
\put(2,.7){\shortstack[c]{$\vec e_{2}$}}
\put(1, 1.5){\vector(0, -1){1}}
\put(1,.2){\shortstack[c]{$\vec e_{3}$}}
%
\put(1, 1.5){\vector(4, 3){3}}
\put(2.3, 2.7){\shortstack[c]{$x$}}
%
\put(4, 3.75){\vector(-1, -4){0.4}}
\put(5.8, 3.9){\shortstack[c]{$\vec b_{1}$}}
\put(4, 3.75){\vector(1, 0){2.0}}
\put(3.7, 2.0){\shortstack[c]{$\vec b_{2}$}}
\put(4, 3.75){\vector(2, -3){1.0}}
\put(5.1, 2){\shortstack[c]{$\vec b_{3}$}}
%\put(3.4,3.3){\shortstack[c]{$\vec b_{1}$}}
\end{picture}
}
\caption{Hexrotor UAV relation of inertial and body-fixed reference frames.}\label{fig:hexrotorDiagram}
\end{figure}

\subsection{Equations of Motion}

The direction of thrust at each rotor is illustrated in Figure~\ref{fig:hexrotorThrust}.
We introduce the thrust-based frame $\{\vec t_1,\vec t_2,\vec t_3\}$ that is fixed to the hexrotor body such that each axis is parallel to the direction of thrust of each rotor. For example, the positive thrust of the first propeller is along the second thrust-based axis $\vec t_2$. The rotation matrix $Q\in\SO$ representing the linear transformation from the thrust-based frame to the body-fixed frame is given by
%
%the rotors produce thrust according the the orthonormal vectors $\{\vec x,\vec y,\vec z\}$; this frame is fixed to the body such that the relative attitude configuration with respect to the body-fixed referenced frame is fixed with $R^*\in\SO$ such that $\{\vec b_1,\vec b_2,\vec b_3\}=R^*\{\vec x,\vec y,\vec z\}$. Hence, according to the hexrotor UAV geometry,
\begin{align}
\label{eqn:Q}
Q=\begin{bmatrix}
-\frac{1}{\sqrt2} & 0 & \frac{1}{\sqrt2}\\
-\frac{1}{\sqrt6} & \sqrt{\frac{2}{3}} & -\frac{1}{\sqrt6}\\
-\frac{1}{\sqrt3} & -\frac{1}{\sqrt3} & -\frac{1}{\sqrt3}
\end{bmatrix},
\end{align}
where the $i$-th column of $Q$ corresponds to the direction of the $i$-th thrust-based axis $\vec t_i$ with respect to the body-fixed frame.

Let $f_i\in\Re$ be the thrust generated by the $i$-th propeller, and let $f=[f_1,f_2,\ldots,f_6]^T\in{\Re}^6$. It is commonly assumed that the reaction torque at each propeller is directly proportional to the thrust, i.e. $\tau_i = c f_i$ for a positive constant $c$. According to the configuration of propellers illustrated in Figure~\ref{fig:hexrotorThrust}, the total thrust $F\in{\Re}^3$ and the total moment $M\in{\Re}^3$, represented with respect to the body-fixed frame can be written as
\begin{align}
F&=
Q\begin{bmatrix}
0 & 0 & 1 & 0 & 0 & -1 \\
1 & 0 & 0 & -1 & 0 & 0 \\
0 & -1 & 0 & 0 & 1 & 0
\end{bmatrix}f\triangleq A_F f,\label{eqn:Fmat}\\
M&=
Q\begin{bmatrix}
-l & -l & c & -l & -l & c \\
c & -l & -l & c & -l & -l \\
-l & c & -l & -l & c & -l
\end{bmatrix}f\triangleq A_M f,\label{eqn:Mmat}
\end{align}
%where the distance $l$ is defined as the distance between the center of each propeller and the closest thrust-based axis, and it is illustrated at Figure~\ref{fig:hexrotorThrust}. \EditTL{TODO: specify the direction of propeller rotation, and change the sign of $c$ accordingly.}
%The direction of propeller rotation is aligned with positive propeller thrust. So, the reaction propeller drag torque is aligned with negative propeller thrust and opposite to positive propeller thrust; hence the signs of $c$ in Equation \ref{eqn:Mmat} are dependent on the signs of the components of vector $f$.
As $c\ll l$, the reaction torque is ignored in this paper, and it is assumed that $c=0$. It can be shown that the determinant of the matrix $\begin{bmatrix}A_F\\A_M\end{bmatrix}$ is $16l^3$, and therefore it is invertible if $l\neq 0$. Therefore, for given total thrust $F$ and total moment $M$, the thrust of each rotor $f$ can be obtained by \refeqn{F} and \refeqn{M}. Using this, the control input of the presented hexrotor UAV is considered as $(F,M)$ in this paper.

%We consider the thrust in the directions depicted in Figure \ref{hexrotorThrust}. Drag due to the propellers generates a torque, which is assumed linear with respect to thrust. Because the propellers are variable pitch, the thrust may be positive or negative, but the torque remains in the same direction as the angular velocity of the propeller blades remains in the same direction. For the $i-th$ propeller that produces force $f_i$, its torque can be written as $\tau_i=c^*f_i$ where $c^*=-sgn(f_i)c$ for positive fixed constant $c$. Hence, in the body-fixed frame, the forces $F\in{\Re}^3$ and moments $M\in{\Re}^3$ are related to propeller thrusts $f\in{\Re}^6$ using $A$ defined by $A_F$ and $A_M$ such that
%\begin{gather}
%A_F=R^*
%\begin{bmatrix}
%0 & 0 & 1 & 0 & 0 & -1 \\
%1 & 0 & 0 & -1 & 0 & 0 \\
%0 & -1 & 0 & 0 & 1 & 0
%\end{bmatrix}\\
%A_M=R^*
%\begin{bmatrix}
%-l & -l & c^* & -l & -l & c^* \\
%c^* & -l & -l & c^* & -l & -l \\
%-l & c^* & -l & -l & c^* & -l
%\end{bmatrix}\\
%A=\begin{bmatrix}
%A_F \\ A_M
%\end{bmatrix}\\
%\begin{bmatrix}
%F \\ M
%\end{bmatrix}
%=
%A
%f
%\end{gather}
%where $l$ is defined in Figure \ref{hexrotorThrust}. The determinant depends on the sign $c^*$; however, considering $c^*\approx0$ because $l\gg \norm{c^*}$, the determinant of the above matrix is $16l^3$ and is invertible for $l\neq0$.
%\definecolor{red}{rgb}{1,0,0}
\begin{figure}
\centerline{
	\setlength{\unitlength}{0.1\columnwidth}\scriptsize
\begin{picture}(7,7)(0,0)
\put(0,0){\includegraphics[width=0.8\columnwidth]{hexrotorThrust_t123.png}}
\put(2.8,3.4){\shortstack[c]{\textcolor{red}{$\vec b_{1}$}}}
\put(4.25,4.25){\shortstack[c]{\textcolor{red}{$\vec b_{2}$}}}
\put(4.25,3.3){\shortstack[c]{\textcolor{red}{$\vec b_{3}$}}}
%
%
\put(1.8,3.5){\shortstack[c]{$\vec f_{1}$}}
\put(1.85,2.8){\shortstack[c]{$\vec \omega_{1}$}}
%
\put(3.4,4.6){\shortstack[c]{$\vec f_{2}$}}
\put(2.5,4.8){\shortstack[c]{$\vec \omega_{2}$}}
%
\put(4.9,4.2){\shortstack[c]{$\vec f_{3}$}}
\put(4.6,5.1){\shortstack[c]{$\vec \omega_{3}$}}
%
\put(5.3,2.75){\shortstack[c]{$\vec f_{4}$}}
\put(5.6,3.5){\shortstack[c]{$\vec \omega_{4}$}}
%
\put(4.55,1.2){\shortstack[c]{$\vec f_{5}$}}
\put(5.15,1.6){\shortstack[c]{$\vec \omega_{5}$}}
%
\put(2.5,1.5){\shortstack[c]{$\vec f_{6}$}}
\put(3.4,1.6){\shortstack[c]{$\vec \omega_{6}$}}
\put(7.1,1.2){$\vec t_1$}
\put(4.2,6.4){$\vec t_2$}
\put(0.9,1.4){$\vec t_3$}
\end{picture}
}
\caption{The hexrotor UAV configuration consists of six actuators (rigidly connected to the frame) that produce thrust (positive direction pictured) aligned with the axes of the thrust-based frame, which is fixed with respect to both body-fixed referenced frame as shown. The rotation of the propellers is in the same direction regardless of the sign of thrust.}\label{fig:hexrotorThrust}
\end{figure}

%\begin{figure}
%\centerline{
%	\includegraphics[width=0.8\columnwidth]{hexrotorThrust}}
%
%\caption{The actuators produce thrust (positive direction pictured) according to both body-fixed referenced frames. \EditTL{TODO: Regenerate this figure}}\label{fig:hexrotorThrust}
%\label{AllAlgorithms}
%\end{figure}
% ${\vec x,\vec y,\vec z\}$, which can be related to $\{\vec b_1,\vec b_2,\vec b_3\}$ as shown.

%
%\begin{bmatrix}
%F_1 \\ F_2 \\ F_3 \\ M_1 \\ M_2 \\ M_3
%\end{bmatrix}
%&=R^*
%\begin{bmatrix}
%0 & 0 & 1 & 0 & 0 & -1 \\
%1 & 0 & 0 & -1 & 0 & 0 \\
%0 & -1 & 0 & 0 & 1 & 0 \\
%-l & -l & c^* & -l & -l & c^* \\
%c^* & -l & -l & c^* & -l & -l \\
%-l & c^* & -l & -l & c^* & -l
%\end{bmatrix}
%\begin{bmatrix}
%f_1 \\ f_2 \\ f_3 \\ f_4 \\ f_5 \\ f_6
%\end{bmatrix}

The hexrotor equations of motion are given by
\begin{gather}
\dot x=v,\label{eqn:xdot} \\
m\dot v=mge_3+RF+\Delta_x, \label{eqn:vdot}\\
\dot R=R\hat \Omega,\\
J\dot\Omega + \Omega\times J\Omega =M+\Delta_R,\label{eqn:Wdot}
\end{gather}
where the total mass and the inertia matrix are denoted by $m\in\Re$ and $J\in{\Re}^{3\times 3}$, respectively. The gravitational acceleration is denoted by $g\in\Re$, and $e_3=[0,\,0,\,1]^T\in{\Re}^3$. The vector $v\in{\Re}^3$ denotes the velocity of the mass center represented with respect to the inertial frame, and $\Omega\in{\Re}^3$ denotes the angular velocity represented with respect to the body-fixed frame. The \textit{hat map} $\hat\cdot:{\Re}^3\rightarrow\so$ is the linear transformation from $3\times 1$ vectors to $3\times 3$ skew-symmetric matrices defined such that $\hat xy=x\times y$ for any $x,y\in{\Re}^3$~\cite{MarRat99}. Disturbance force and moment are denoted by $\Delta_x,\Delta_R\in{\Re}^3$, respectively, and it is assumed that they are unknown but fixed.

\subsection{Hovering Capability}

According to \refeqn{F}, the presented hexrotor UAV can generate the total thrust along any direction, and provided that the thrust is sufficiently large compared with the total mass, it can hover at arbitrary attitudes. More explicitly, the feasible attitude region for hover is defined for regions of $\SO$ where the maximum thrust is greater than the gravitational force under the constraint that the total moment is zero.

Let $f_{\max}$ be the maximum thrust of each propeller. When $M=0$, the feasible region of the total thrust is given by a cube where the sides of the cube are aligned with the thrust-based frame, and the length of each side is $4f_{\max}$. Therefore, the magnitude of the total thrust is maximized along the line toward each vertex of the cube, and the maximum value is given by
\begin{align*}
\|F\|_{\max} = 2\sqrt{3} f_{\max}.
\end{align*}
If the direction of the total thrust is aligned with any of thrust-based axes, the maximum possible thrust reduces to $2f_{\max}$.

For the given mass $m$ of the hexrotor UAV, these determine the admissible hovering attitudes. The hexrotor UAV can hover at any attitude if $mg<2f_{\max}$, and it is impossible to hover if $2\sqrt{3}f_{\max} <mg$. If $2f_{\max}< mg < 2\sqrt{3}f_{\max}$, there exists a set of admissible directions of gravity with respect to the thrust-based frame as illustrated in Figure \ref{fig:hoverRegions}.

%There exists completely admissible hovering regions if $2f_{\max}>mg$, partially admissible hovering regions if $F_{min}<mg<F_{max}$, and completely inadmissible regions of hover if $F_{max}<mg$. Figure \ref{hoverRegions} illustrates the second aforementioned case, namely when hovering is possible for only certain admissible regions of $\SO$. When the $F$ (blue) is capable of extending beyond the gravity sphere (red), hover is possible.

%If $2f_{\max}< mg$,

%For maximum propeller thrust $f_{max}$, the maximum thrust in any of the rotor thrust directions is $F^*=2f_{max}$.
%Depending on the hexrotor attitude relative to gravity, propellers may only exert thrust such that the resulting $M=0_{3\times1}$ to achieve hover.
%The maximum UAV thrust
%\begin{gather}
%\label{Fmax}
%F_{max}=\sqrt{3}F^*
%\end{gather}
%occurs at the attitude where the load is equally shared between the propellers according to Pythagoreans theorem; however the minimum thrust attitude occurs when only two coplanar propellers provide thrust opposite to gravity, or $F_{min}=F^*$.
%For hexrotor mass $m$,

\begin{figure}
\centerline{
	\subfigure[\;Feasible region of total thrusts]
		{\includegraphics[width=0.45\columnwidth]{CompletelyAdmissibleRegions}}
	\subfigure[\;Gravity sphere]
		{\includegraphics[width=0.45\columnwidth]{CompletelyInadmissibleRegions}}
	}
\centerline{
	\subfigure[\;Connected admissible regions]
		{\includegraphics[width=0.45\columnwidth]{PartiallyAdmissibleRegions_connecting}}
	\subfigure[\;Broken admissible regions]
		{\includegraphics[width=0.45\columnwidth]{PartiallyAdmissibleRegions_notconnecting}}
	}
\caption{The total thrusts that can be generated by the presented hexrotor UAV with respect to the thrust-based frame is illustrated by a blue cube, where the length of each side is four times of the maximum thrust of each propeller, i.e., $4f_{\max}$ (Fig. (a)). To hover at any arbitrary attitude, the sphere of gravity with the radius of $mg$ (Fig. (b)) should be enclosed by the cube, i.e., $mg< 2f_{\max}$. If $2\sqrt{3}f_{\max} < mg$, then it is not possible to hover at any attitude. At the remaining cases where $2f_{\max}<mg<2\sqrt{3}f_{\max}$, the set of gravity directions, with respect to thrust-based frame, that are feasible for hovering is given by the blue regions (Figs. (c),(d)).
%Gravity (red) produces an equal force on the UAV at any attitude; the vector summation of the propeller thrust (blue) with zero moment breaches the gravity sphere in admissible regions of hover. This yields four possible scenarios to determine if hover is possible: the gravitational force is always greater than maximum thrust at every attitude, maximum thrust at any attitude is greater than the gravitational force, some attitude regions are possible and they smoothly connect, and possible hover regions may exist without smoothly connecting.
%\EditTL{Regenerate these figures with \texttt{axis equal} such that the sphere looks like a sphere. The caption should be expanded such that there figures are self-explanatory.}
}\label{fig:hoverRegions}
\end{figure}

	% Converting thrust of each rotor to the total thrust and moment
	% Equations of motion
	% Feasible hovering attitude
		% visualization of the total thrust box and gravity sphere
		% description about the set of attitudes that UAV can hover

\section{Geometric Control of Hexrotor UAV}\label{sec:Control}

In this section, we present a geometric nonlinear controller to track given attitude and position commands.

\subsection{Tracking Problem Formulation}

Let $x_d(t)\in{\Re}^3$ be a desired position trajectory, and let $R_d(t)\in\SO$ be a desired attitude trajectory of the hexrotor UAV. The desired velocity is given by $v_d(t)=\dot x_d(t)$. The desired attitude trajectory satisfies the following kinematics equation:
\begin{align}
\dot R_d = R_d \hat\Omega_d,\label{eqn:Rddot}
\end{align}
where $\Omega_d(t)\in{\Re}^3$ is the desired angular velocity. It is assumed that the desired trajectories are smooth. We design a control input such that the desired trajectories become an exponentially stable equilibrium of the controlled hexrotor UAV.

	% Definition of tracking problem
		% desired position trajectory and attitude trajectory
		% Goal of tracking control

\subsection{Geometric Control on $\SE$}

%For the given hexrotor UAV mode, the attitude dynamics is decoupled from the translational dynamics, and the translational dynamics is affected by the attitude dynamics only through the control force term at \refeqn{vdot}. As such, we can construct a position control system independently to an attitude control system.

We first introduce error variables for the translational dynamics. Let $e_x,e_v\in{\Re}^3$ be the position tracking error and the velocity tracking errors, respectively:
\begin{align}
e_x = x-x_d,\quad e_v= v-v_d.\label{eqn:exev}
\end{align}
The following form of an integral control term is introduced:
\begin{align}
e_i(t) = \int_0^t c_1 e_x(\tau) + e_v(\tau) d\tau,\label{eqn:ei}
\end{align}
for a positive constant $c_1$. Unlike the common integral control term where only the position tracking error $e_x$ is integrated, the velocity tracking error is also integrated. This has a net effect of increasing the proportional gain by $k_i$ since $\dot e_x = e_v$.  This yields a simpler stability analysis, and it has a parallel structure with the new integral control term of the attitude dynamics that is introduced later.

>>>>

\usepackage[]{graphicx}    % We use this package in this document
\newcommand{\ignore}[1]{}  % {} empty inside = %% comment

\usepackage{epstopdf}

\begin{document}
\title{An Example of the 2014 IEEE Aerospace Conference Paper Format Using a \LaTeX~Enivronment}

\author{%
Erica DeIonno\\ 
The Aerospace Corporation\\
El Segundo, CA 90245\\
310-336-8166\\
erica.deionno@aero.org
\and 
Jane Smith\\
Department of ECE\\
University of Nowhere\\
Nowhere, ZS 99999\\
888-888-8888\\
jane.smith@nowhere.edu
%%%% IMPORTANT: Use the correct copyright information--IEEE, Crown, or U.S. government. %%%%%
\thanks{\footnotesize 978-1-4799-1622-1/14/$\$31.00$ \copyright2014 IEEE.}              % This creates the copyright info that is the correct 2012 data
%\thanks{{978-1-4799-1622-1/14/$\$31.00$ \copyright2014 Crown.}}          % Use this copyright notice only if you are employed by a crown government (e.g., Canada, UK, Australia)
%\thanks{{U.S. Government work not protected by U.S. copyright.}}         % Use this copyright notice only if you are employed by the U.S. Government.
%%%%% Use this footnote to keep track of your paper number/versioning.
\thanks{$^1$ IEEEAC Paper \#xxxx, Version x, Updated dd/mm/yyyy.} % NOTE: Modify this line to reflect your paper number, version, and date of version for tracking purposes.
}

@@

\begin{abstract}
This paper serves as an example for the use of the \LaTeX~class file for the 2014 Aerospace Conference. The \LaTeX~class file for the 2014 conference has been modified from that of prior year conferences in order to fix minor bugs and to conform to new formatting requirements. Within the class file there are some customized commands that are illustrated in this paper. They are: tableofcontents, acknowledgments, thebiography. There are also comments sprinkled throughout the~.tex file to illustrate the usage of the class file. If you have difficulties or errors using this class file, please contact me at the e-mail address in the author's information slot. Some of the content below is filler designed to show you how a properly formatted paper should look. Read the official ``Author's Instructions for the 2014 IEEE Aerospace Conference'' to find the full description of the paper formatting requirements.
\end{abstract}

@@
